Time Series Bootstrapping For Solar Current

### 2021-12-06 deliverables/paper.Rmd
Added function for creating bootstrap blocks from df

```{r filter}
HOUR_WINDOW <- 11:16
df_high_irradiance <- df[df$Hour %in% HOUR_WINDOW,]
filtered_current_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$current_out)) +
  theme_bw()
print(filtered_current_hist)
```

@@

>>>>

```{r filter}
HOUR_WINDOW <- 11:16
df_high_irradiance <- df[df$Hour %in% HOUR_WINDOW, ]
filtered_current_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$current_out)) +
  theme_bw()
print(filtered_current_hist)
```

@@

#' Given a dataframe, return a matrix of bootstrap blocks
#'
#' @param df A dataframe of irradiance values
#' @return A matrix whose rows are bootstrap blocks
make_blocks_from_df <- function(df) {
  df <- df %>%
    mutate(date = lubridate::make_date(Year, Month, Day))
  # The number of blocks is the number of days
  number_of_blocks <- length(unique(df$date))
  # The length of a block is the number of
  # observations in each individual day.
  # In this case, we can simply look at the first one,
  # because all of the days have the same number of observations
  length_of_block <- nrow(df[df$date == unique(df$date)[1], ])
  blocks <- matrix(NA, nrow = number_of_blocks, ncol = length_of_block)
  print(dim(blocks))
  for (i in 1:number_of_blocks) {
    blocks[i, ] <- df$current_out[(i - 1) * length_of_block + 1 : (i * length_of_block)]
  }
  return(blocks)
}
# We have to use the modified DataFrame here,
# or else the assumptions about block size don't hold
make_blocks_from_df(df_high_irradiance)
